Phenology and Mycorrhizae Manuscript

### 2023-01-30 manuscriptCode_phenologyAndMycorrhizae.Rmd
Added code to process and gap-fill NEON air temperature at various heights of the tower

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath)
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=mean,funName="mean")
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=min,funName="min")
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=max,funName="max")
```

#Triple Air Temperature at Top of Canopy
```{r,eval=FALSE} 
##Need to redownload!! 
dataName="NEON_TopTemperatureData"
NEON_ID='DP1.00003.001'
selectColumns <- c('tempTripleMean','finalQF')
inFileName <- "TAAT_30min.csv"
varName <- 'tempTripleMean'
if(!file.exists(paste0(dataPath,"/",dataName))){
  dir.create(paste0(dataPath,"/",dataName))
}

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath)
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=mean)
gapFillFromDaymet(dataName=dataName,dataPath=dataPath,varName=varName)

@@

>>>>

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath)
for(funName in c("mean","max","min")){
  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=mean,funName=funName)
  #Calculate LRs
  gapFillFromDayMet_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funName)
}

@@

<!-- #Triple Air Temperature at Top of Canopy -->
<!-- ```{r,eval=FALSE}  -->
<!-- ##Need to redownload!!  -->
<!-- dataName="NEON_TopTemperatureData" -->
<!-- NEON_ID='DP1.00003.001' -->
<!-- selectColumns <- c('tempTripleMean','finalQF') -->
<!-- inFileName <- "TAAT_30min.csv" -->
<!-- varName <- 'tempTripleMean' -->
<!-- if(!file.exists(paste0(dataPath,"/",dataName))){ -->
<!--   dir.create(paste0(dataPath,"/",dataName)) -->
<!-- } -->

<!-- downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID) -->
<!-- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns, -->
<!--                 inFileName=inFileName,dataPath=dataPath) -->
<!-- calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=mean) -->
<!-- gapFillFromDaymet(dataName=dataName,dataPath=dataPath,varName=varName) -->

<!-- ``` -->
